\documentclass[stu]{apa7}
\title{Create Task - Status Update 1}
\author{Anish Goyal} 
\let\comma,
\authorsaffiliations{Gwinnett School of Math\comma{} Science\comma{} and Technology}
\shorttitle{Status Update 1}
\course{AP Computer Science Principles - 1st Period}
\professor{Ben Schepens}
\duedate{March 27, 2023}
\newcommand{\HRule}{\rule{\linewidth}{0.25mm}}
\setlength\parindent{36pt}
\authornote{The assignment was to submit a status update of their create task covering some questions about their project.}

\begin{document}
\maketitle
\tableofcontents
\newpage
\section{How much programming do you have left to complete?}
I have completed all the programming tasks required for the project, and all the features and functionalities are working as intended. I have thoroughly tested the program and have fixed any bugs or errors that I encountered during the development process. I am glad that I did \emph{not} complicate the Create Task as it made the project much easier to complete and my AP reader will have an easier time reading my code. 

\section{Have you "graded" yourself based on the grading rubric?  What score did you give yourself?}
Yes, I have reviewed the grading rubric and evaluated my project based on its criteria. I have met or exceeded the expectations for each section of the rubric. Based on my evaluation, I have given myself the highest score possible, as I have completed all the required components of the project and they are working as intended.

\section{What problems/issues do you need to address to complete the project successfully by Friday 3/31?}
Because I have already completed the project without any issues, I do not have any problems or issues that need to be addressed to meet the deadline of Friday 3/31.

\end{document}