\documentclass[man]{apa7}
\usepackage{lipsum}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber]{biblatex}
\addbibresource{references.bib}
\title{Persuasive Narrative Checkpoint}
\shorttitle{Persuasive Narrative Checkpoint}
\author{Anish Goyal}
\let\comma,
\affiliation{Gwinnett School of Math\comma{} Science\comma{} and Technology}
\date{\today}
\newcommand{\HRule}{\rule{\linewidth}{0.25mm}}
\setlength\parindent{36pt}
\begin{document}
\maketitle
\tableofcontents
\newpage
\section{Narrowed Topic}
\hspace{\parindent} The use of OpenAI's GPT model and its derivatives in education and creativity. Promoting the use of artificial intelligence in writing and research as an educational utility rather than a cheating tool.

\section{Working Two-Part Title}
\hspace{\parindent} Natural Language Processing With GPT3: More than just a cheating tool

\section{Working Introduction and Thesis}
\hspace{\parindent} As Professor Johnson sat in front of his computer, scrolling through endless pages of research, he couldn't help but feel overwhelmed. The amount of information available was staggering and the task of sifting through it all seemed impossible. That's when he stumbled upon OpenAI's GPT model. \emph{I had heard of it before,} he thought to himself, \emph{but never really looked into it.} As he began to experiment with the language model, he couldn't believe how easily it was able to understand and respond to his queries. "This could change everything," he exclaimed as he excitedly shared his discovery with his colleagues. In the classroom, the students were amazed as they watched GPT generate essays and research papers with ease. "This is so cool!" said one student as she watched her essay on the effects of climate change take shape in front of her eyes. "I never knew writing could be so easy," said another. The students were more engaged and excited about their work than ever before. The model not only made their work more efficient, but it also sparked new levels of creativity and engagement. They couldn't wait to see where this technology would take them next.
\newpage
\nocite{*}
\printbibliography
\end{document}