\section{Objective 24}
\subsection{Terminology}
\frame{\subsectionpage}
\begin{frame}{Definitions}
    \begin{itemize}
        \item<1-2>{A \textcolor{orange}{\textbf{vector}} is a quantity that has both a magnitude and a direction.}
        \item<2>{The \textcolor{orange}{\textbf{intersection}} of two vectors is the point where they meet.}
    \end{itemize}
\end{frame}
\subsection{Objective Defined}
\frame{\subsectionpage}
\begin{frame}{What is Objective 24?}
    \begin{block}{Objective Definition}
        In this objective, you must be able to... \\
        \color{orange}{``Find points of intersection of intersecting vectors.``}
    \end{block}
\end{frame}
\begin{frame}{But what does that mean?}
    \begin{itemize}
        \item<1-2>{Well, in baby terms...}
        \begin{itemize}
            \item<2>{We want to find where any number of vectors cross.}
        \end{itemize}
    \end{itemize}
\end{frame}
\subsection{\textit{Modus Operandi}}
\frame{\subsectionpage}
\begin{frame}{Formula}
    \begin{block}{Formula}
        \uncover<1->{Let \begingroup\color{orange}{\bm{$\vec{r_1}(t)$}}\endgroup \ and \begingroup\color{orange}{\bm{$\vec{r_2}(s)$}}\endgroup \ be two vector-valued functions in the form:}
            \begin{align*}
                \uncover<2->{\vec{r_1}(t) = r_1 + t\vec{v_1}} \\
                \uncover<3->{\vec{r_2}(s) = r_2 + s\vec{v_2}}
            \end{align*}
        \uncover<4->{Then their point of intersection can be found by solving for \begingroup\color{orange}{\bm{$t$}}\endgroup \ and \begingroup\color{orange}{\bm{$s$}}\endgroup \ such that \begingroup\color{orange}{\bm{$\vec{r_1}(t) = \vec{r_2}(s)$}}\endgroup.}
    \end{block}
\end{frame}
\begin{frame}{Formula}
    \begin{block}{Formula (cont.)}
        \uncover<1->{Where:}
        \begin{itemize}
            \item<2->{\begingroup\color{orange}{\bm{$\vec{r_1}(t)$}}\endgroup \ and \begingroup\color{orange}{\bm{$\vec{r_2}(s)$}}\endgroup \ are the vector-valued functions of the two lines}
            \item<3->{\begingroup\color{orange}{\bm{$t$}}\endgroup \ and \begingroup\color{orange}{\bm{$s$}}\endgroup \ are the parameters used to determine the point of intersection}
            \item<4->{\begingroup\color{orange}{\bm{$r_1$}}\endgroup \ and \begingroup\color{orange}{\bm{$r_2$}}\endgroup \ are the starting points of the lines}
            \item<5>{\begingroup\color{orange}{\bm{$\vec{v1}$}}\endgroup \ and \begingroup\color{orange}{\bm{$\vec{v2}$}}\endgroup \ are the direction vectors of the lines}
        \end{itemize}
    \end{block}
\end{frame}
\subsection{Explanation}
\frame{\subsectionpage}
\begin{frame}{Explanation}
    \uncover<1->{\textbf{So, what was all of that?}}
    \begin{itemize}
        \item<2->{By equating the two vector equations and solving for the parameters \begingroup\color{orange}{\bm{$t$}}\endgroup \ and \begingroup\color{orange}{\bm{$s$}}\endgroup , we can determine the point where the two lines intersect.}
        \item<3->{This works because the point of intersection must be on both lines simultaneously.}
    \end{itemize}
\end{frame}
\begin{frame}{Explanation}
    \textbf{That's great and all, but when are you going to tell us how to solve it?} \\
    \uncover<2->{Okay, okay! The best way to show you is with an example.}
\end{frame}
\subsection{Example}
\frame{\subsectionpage}
\begin{frame}{Example}
    \textbf{Example}
    \begin{block}{Problem}
        Two lines 
        \begin{align*}
            \textbf{v} = \begin{pmatrix} 7 \\ -3 \\ 1 \end{pmatrix} + \begin{pmatrix} -2 \\ 5 \\ 1 \end{pmatrix} t \text{ and } \textbf{w} = \begin{pmatrix} 8 \\ -1 \\ -1 \end{pmatrix} + \begin{pmatrix} 1 \\ -4 \\ 0 \end{pmatrix}s
        \end{align*} 
        intersect at a point. Find the coordinates of the point of intersection.
    \end{block}
\end{frame}
\begin{frame}{Example}
    \textbf{First, we need to find the vector equations for the lines. This can be done by adding each parameter to the specified coordinate:}
    \begin{align*}
        \uncover<2->{v = \langle 7-2t, -3+5t, 1+t \rangle} \\
        \uncover<3->{w = \langle 8+s, -1-4s, -1 \rangle}
    \end{align*}
\end{frame}
\begin{frame}{Example}
    \textbf{Now, set the two vectors equal to each other:}
    \begin{align*}
        \uncover<2->{\langle 7-2t, -3+5t, 1+t \rangle = \langle 8+s, -1-4s, -1 \rangle}
    \end{align*}
\end{frame}
\begin{frame}{Example}
    \textbf{It follows that if the two vectors are equal, their components must be equal:}
    \begin{equation*}
        \uncover<2->{\systeme {
            7-2t=8+s,
            -3+5t=-1-4s,
            1+t=-1
        }}
    \end{equation*}
    \uncover<3->{\textbf{Notice how we have a system of equations!}}
\end{frame}
\begin{frame}{Example}
    \textbf{So, let's solve for a parameter (in this case, \begingroup\color{orange}{\bm{$t$}}\endgroup):}
    \begin{align*}
        \uncover<2->{1+t = -1 \implies t = -2}
    \end{align*}
    \uncover<3->{\textbf{Now that we know \begingroup\color{orange}{\bm{$t$}}\endgroup, we can substitute it into the first vector equation to find the point of intersection.}}
\end{frame}
\begin{frame}{Example}
    \textbf{Recall that our vector equation for \begingroup\color{orange}{\bm{$v$}}\endgroup \ was:}
    \begin{align*}
        \uncover<2->{v = \langle 7-2t, -3+5t, 1+t \rangle}
    \end{align*}
    \uncover<3->{\textbf{Since we're assuming that \begingroup\color{orange}{\bm{$v$}}\endgroup \ and \begingroup\color{orange}{\bm{$w$}}\endgroup \ already intersect, we only need to find one parameter and plug it back into its corresponding vector equation.}}
\end{frame}
\begin{frame}{Example}
    \textbf{So, let's substitute \begingroup\color{orange}{\bm{$t=-2$}}\endgroup \ into \begingroup\color{orange}{\bm{$v$}}\endgroup :}
    \begin{align*}
        \uncover<2->{v = \langle 7-2(-2), -3+5(-2), 1+(-2) \rangle = \begin{pmatrix} 11 \\ -13 \\ -1 \end{pmatrix}}
    \end{align*}
    \uncover<3->{\textbf{Therefore, the point of intersection is \begingroup\color{orange}{\bm{$(11, -13, -1)$}}\endgroup.}} \\
    \uncover<4->{\textbf{Alternatively, we could have substituted \begingroup\color{orange}{\bm{$s$}}\endgroup \ into \begingroup\color{orange}{\bm{$w$}}\endgroup. Always make sure you are plugging in the correct parameter into the correct vector equation.}}
\end{frame}
\begin{frame}{Example}
    \textbf{A substandard visual}
    \uncover<2->{\begin{tikzpicture}
        \begin{axis}[axis equal,
                     axis lines=middle,
                     xlabel=$x$,
                     ylabel=$y$,
                     zlabel=$z$,
                     xmin=-5, xmax=15,
                     ymin=-15, ymax=5,
                     zmin=-2, zmax=5,
                     clip=false]
          % Define the two lines as parametric vectors
          \addplot3[blue, variable=\t, domain=0:-2] ({7-2*t},{-3+5*t},{1+t});
          \addplot3[red, variable=\s, domain=0:3] ({8+s},{-1-4*s},{-1});

          % Find the point of intersection
          \coordinate (A) at (axis cs:11,-13,-1);
          
          % Draw the point of intersection
          \filldraw [black] (A) circle (2pt);
          \node [above right] at (A) {$(11,-13,-1)$};
        \end{axis}
    \end{tikzpicture}}
\end{frame}
\subsection{Gaussian Elimination}
\frame{\subsectionpage}
\begin{frame}{Gaussian Elimination}
    \textbf{What is Gaussian Elimination?}
    \begin{itemize}
        \item<2->{A method of solving a system of linear equations.}
        \item<3->{A method of reducing a system of equations to a triangular matrix.}
        \item<4->{A method of reducing a system of equations to a diagonal matrix.}
    \end{itemize}
\end{frame}
\begin{frame}{Gaussian Elimination}
    \textbf{Why is Gaussian Elimination useful for this objective?}
    \begin{itemize}
        \item<2->{Currently, we've only been dealing with the intersections of 3-dimensional vectors.}
        \item<3->{But what if we wanted to find the intersection of an \begingroup\color{orange}{\bm{$n$}}\endgroup -dimensional vector \begingroup\color{orange}{\bm{$\vec{v}$}}\endgroup \ such that \begingroup\color{orange}{\bm{$\vec{v}$}} \endgroup \ is spanned over all real numbers (\begingroup\color{orange}{\bm{$\vec{v} \in \mathbb{R}^n$}}\endgroup )?}
        \item<4->{Alternatively, what if we wanted to solve for the intersection of more than two vectors?}
        \item<5->{This would make our system of equations quite complicated, and we wouldn't be able to solve it by hand... that is, unless we use Gaussian Elimination.}
    \end{itemize}
\end{frame}
\begin{frame}
    \frametitle{Reduced row echelon form (RREF)}
    \underline{Definition:} To be in RREF, a matrix $A$ must satisfy the following 4 properties (if it satisfies just the first 3 properties, it is in REF):
    \begin{enumerate}[1.]
        \item<2->{If a row does not have only zeros, then its first nonzero number is a $1$. We call this a {\em leading $1$}.}
        \item<3->{The rows that contain only zeros (if there are any) are at the bottom of the matrix.}
        \item<4->{In any consecutive rows that do not have only zeros, the leading $1$ in the lower row is farther right than the leading $1$ in the row above.}
        \item<5->{Each column that contains a leading $1$ has zeros everywhere else in that column.}
    \end{enumerate}
\end{frame}
\begin{frame}{Write out the augmented matrix}
    A system of linear equation is generally of the form
    \begin{equation}
        \label{e.linear}
        A \, \x = \b \,,
    \end{equation}
    where $A \in M(n \times m)$ and $\b \in \R^n$ are given, and $\x=(x_1, \dots, x_m)^T$ is the vector of unknowns.  For example, the system
    \begin{align*}
        x_2 + 2 \, x_3 - x_4 & = 1 \\
        x_1 + x_3 + x_4 & = 4 \\
        -x_1 + x_2 - x_4 & = 2 \\
        2 \, x_2 + 3 \, x_3 - x_4 & = 7
    \end{align*}
    can be written in the form \eqref{e.linear} with...
\end{frame}
\begin{frame}{Write out the augmented matrix}
    \begin{equation*}
        A = 
        \begin{pmatrix}
        0 & 1 & 2 & -1 \\
        1 & 0 & 1 & 1 \\
        -1 & 1 & 0 & -1 \\
        0 & 2 & 3 & -1
        \end{pmatrix} \,,
        \qquad \b =
        \begin{pmatrix}
        1 \\ 4 \\ 2 \\ 7 
        \end{pmatrix} \,.
      \end{equation*}
      \uncover<2>{Once you have the augmented matrix, you need to perform elementary row operations to get the matrix into RREF/REF. Then, you can solve for the unknowns.}
      \uncover<3>{However, I will not be going any more in depth into Gaussian Elimination becaue it is out of the scope for this presentation and I don't want to kill myself writing \LaTeX \ any further.}
\end{frame}
\subsection{Objective Summary}
\frame{\subsectionpage}
\begin{frame}{Objective Summary}
    \textbf{To find the point of intersection between two vectors:}
    \begin{itemize}
        \item<2->{Find the vector equations for each vector.}
        \item<3->{Set the two vectors equal to each other.}
        \item<4->{Solve for a parameter.}
        \item<5->{Substitute the parameter into one of the vector equations to find the point of intersection.}
    \end{itemize}
\end{frame}